Spin canonical divisors of log stacky curves

### 2015-06-27 stacky_write_up/spin_cring.tex

This suggests how we can recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  Define 
\[
	S_0 = \{u^l : l\in \mathbb{Z}^{\ge 0}\}
\]
and for $i \in \mathbf{N}$, if $c_j$ is the maximal element among of $c_1, \ldots c_n$ at most $i$ (note that this always exists since $1=c_1\le i$), define
\[
	S_i = y_j S_{i-j}.
\]
Then define 
\[
	S = \cup_{i=1}^{\infty} S_i.
\]
A quick computation checks that $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, so we have proven part (a).

@@

\begin{rem}\label{rem:quad-gen}
If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_ii}$ for some odd $3\le e_i\in \mathbf{N}$, then $T$ from the previous lemma consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
\end{rem}

>>>>

This suggests how we can recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$.  Define 
\[
	S_0 = \{u^l : l\in \mathbb{Z}^{\ge 0}\}
\]
and for $i \in \mathbb{N}$, if $c_j$ is the maximal element among of $c_1, \ldots c_n$ at most $i$ (note that this always exists since $1=c_1\le i$), define
\[
	S_i = y_j S_{i-j}.
\]
Then define 
\[
	S = \cup_{i=1}^{\infty} S_i.
\]
A quick computation checks that $S$ forms a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$, so we have proven part (a).

@@

\begin{rem}\label{rem:quad-gen}
If $\frac{\alpha}{\beta}=\frac{e_i-1}{2 e_ii}$ for some odd $3\le e_i\in \mathbb{N}$, then $T$ from the previous lemma consists only of terms of the form $x_i y_j$ and $y_i y_j$, which are quadratic in the generators.
\end{rem}
